An Evolutionary Quantitative Genetic Model of the Negative Selection Process in Humans

### 2023-06-29 manuscript/manuscript.tex
ms updates
methods

\documentclass[11pt]{article}
\RequirePackage{fullpage}
%\RequirePackage[font=small,labelfont=bf]{caption}
\RequirePackage{amsmath,amssymb,amsthm}
\RequirePackage{graphicx}
\RequirePackage[hidelinks]{hyperref}
\RequirePackage{subcaption}
\RequirePackage{wasysym}
\RequirePackage{authblk}
\RequirePackage{bm}
\RequirePackage{bbm}
%\RequirePackage[osf]{mathpazo}
\let\temp\rmdefault
\RequirePackage{mathpazo}
\let\rmdefault\temp

@@

\title{Towards a Complete Model of the Negative Selection Process in Humans}

@@

When mutations are only weakly deleterious, their allele frequencies are
strongly influenced by stochastic perturbations and their frequency
trajectories are no longer well-approximated by deterministic models. When
genetic drift is the only source of randomness in allele frequency change, the
relevant scale of stochastic perturbations is determined by the drift-effective
population size $N_e$ (e.g. due to only non-selective process). The insight of
nearly neutral theory (XXX) was that the qualitative behavior of selected sites
is determined by the compound parameter $2N_e s$. When $2N_e s \gg 1$, the
stochastic component of allele frequency change is minuscule relative to
selection and can be ignored; this is why the factor that rescales the
drift-effective population size under the BGS model does not depend on $N_e$.
However, when $2N_e s \le 1$, the stochastic perturbations are on a scale equal
to or greater than the changes due to selection. In this regime, weakly
deleterious alleles can drift up to intermediate frequencies before their
eventual loss or fixation. When this occurs, classic BGS theory breaks down for
several reasons. First, the ``delay phase" is no longer negligible as lineages
carrying weakly deleterious mutations can persist on coalescent timescales.
This distorts genealogies away those expected under neutrality
\parencite{Przeworski1999-mb,OFallon2010-my,Higgs1995-xc}. Second, the
distribution of the number of deleterious mutations (and its corresponding
fitness distribution) are no longer stationary and become a traveling wave
\parencite{Rouzine2008-qz,Good2013-lp,Gessler1995-hz} towards reduced
population fitness (since beneficial and back mutations are ignored).
Consequently, individuals in the least-loaded class are stochastically lost,
fixing those mutations with a click of ``Muller's ratchet"
\parencite{Muller1964-ki}. Determining both the rate of Muller's ratchet
\parencite{Haigh1978-gt,Gordo2002-dr,Gessler1995-hz} and the shape of
genealogies under weak selection have been stubborn open problems in
evolutionary genetics.

@@

\begin{align}
    \label{eq:simple_Ne}
    N_e = \frac{2N}{V + 2}
\end{align}

However, unlike non-heritable variation in offspring number, the heritable
variation is autocorrelated across generations. At the individual level
Robertson considered, this is because offspring from large families tend to
beget many descendents themselves (and likewise with small families). The same
autocorrelation occurs at the genomic level, as the perturbations to a neutral
allele's trajectory from its particular fitness background tend to occur in the
same direction across generations as long as the linkage exists and the
selective environment is constant. The additional heritable variation in
offspring number is the additive fitness variation $V_A$, which is inflated by
a factor $Q_t^2$ due to the build up of autocorrelation to generation $t$. We
let $Q^2 := Q_t^2$ as $t \to \infty$. Intuitively, the product $V_A Q^2$
represents the expected total variance in reproductive success a neutral
mutation experiences over its lifetime in a system with weak selection draft.
Incorporating the impact of time-invariant autocorrelation created by draft as
a rescaled rate of drift is analogous to using the Green--Kubo relation to find
the transport coefficient in molecular dynamics with velocity autocorrelation
\parencite{Green1954-kl,Kubo1957-va}.

@@

(c.f. \cite{Robertson1961-ho,Santiago1995-hx}; see XXX for a proof). In
general, however, statistics such as heterozygosity depend on the cumulative
autocorrelation factor \emph{up to some time} $t$, $Q_t^2$ \parencite[p.
2111]{Santiago1998-bs}. This reflects the fact that effective population size
experienced by a mutation newly associated with a fitness background is larger
than the asymptotic effective population size, since not much autocorrelation
has accumulated in the stochastic perturbations caused by drift yet. From a
backwards-time perspective, this reflects the fact that pairwise diversity
(which is approximately heterozygosity when $2N\mu \ll 1$) depends on the
pairwise coalescence rate per generation, which is not constant under draft.
The benefit of using Robertson's forward-time model of draft is that the
inflation factor is invariant with respect to the particular fitness background
the neutral allele becomes stochastically associated with. By contrast, the
difficulty with modeling draft backwards in time is that the coalescence rates
experienced by a lineage are not invariant to which lineage was sampled due to
its particular associated fitness background.

Equation \eqref{eq:main_Ne} is general, since different modes of selection and
linkage can be accommodated by different expressions for the inflation factor
$Q^2$ \parencite{Santiago1995-hx,Santiago1998-bs}. When fitness variation has a
multiplicative polygenic basis, as it does for genome-wide negative selection
processes, the draft asymptotic effective population size experienced by an
arbitrary neutral site under the influence of all linked regions is,

@@

where the factor of one-half comes from ignoring weak associations from
unlinked regions and chromosomes (see XXX). In our genome-wide model, we
consider the summation in Equation \eqref{eq:polygenic_Ne} over non-overlapping
segments $i \in \{1, 2, \ldots, n\}$ each undergoing selection such that
segment $i$ contributes additive fitness variance $V_{A,i}$ to the total
additive genetic fitness variance. Under equilibrium levels of fitness
variation, the autocorrelation function for a neutral allele associated with
segment $i$ is $C(t) = [(1-r_i)(1-\kappa_i)]^t$, where $r_i$ is the
recombination fraction to the segment and $\kappa_i$ is the rate that the
associated fitness variance decays due to selective dynamics. Then, the
cumulative autocorrelation is,

\begin{align}
    Q_i &= 1 + \sum_{j=1}^\infty \left[(1-r_i)(1-\kappa_i)\right]^j \\
        &= \frac{1}{\kappa_i + r_i(1-\kappa_i)}.
\end{align}

@@

which is identical to the genome-wide model of background selection used in
previous studies \parencite{McVicker2009-ax,Elyashiv2016-vt,Murphy2022-sj}.
Thus, the classic background selection model is a special case of the more
general theory of Santiago and Caballero (\citeyear{Santiago2016-mu}), which
they have shown previously (\citeyear{Santiago1998-bs}).

When selection is weak, however, the additive fitness variance under the
classic BGS model is no longer accurate. \textcite{Santiago2016-mu} suggested
that this is due to the loss of fitness variation that occurs when a
segregating site fixes and its heterozygosity becomes zero. If we let $R$
represent the rate of the ratchet of deleterious mutations in fixations per
generation, each fixation removes the equivalent amount of equilibrium
variation put in by mutation. Thus, the steady-state genic variance under
mutation and negative selection is (omitting the segment index $i$ for
clarity),

@@

where the condition $V_a \ge 0$ is met when the probability of fixation is less
than or equal to the neutral fixation probability of $\nicefrac{1}{2N}$, which
is held when considering deleterious mutations. This equation connects the
equilibrium additive genic fitness variance to the flux of new variation in due
to new deleterious mutations and the flux out due to their substitution and the
decline in mean population fitness. When $R=0$, the selection is so strong it
cannot fix, and the equilibrium fitness variation is due entirely to young rare
mutations before their extinction $V_a = V_a^{BGS} = Us$. Santiago and
Caballero demonstrate Equation \eqref{eq:Va} through Fisher's Fundamental
Theorem of Natural Selection, but we find an alternative proof
(\cite{Higgs1995-xc}; see Supplementary Materials Section
\ref{supp:weak-strong}). We find that the steady-state additive genic variance
in Equation \eqref{eq:Va} also results from diffusion models with a flux of
mutations into discrete sites (\cite{Kimura1969-jw}).

@@

While using Equation \eqref{eq:Va} in Equation \eqref{eq:main_Ne} leads to a
prediction for the draft-effective population size $N_d$, closed-form
expressions for the rate of the ratchet $R$ have generally been hard to find
\parencite{Haigh1978-gt,Higgs1995-xc,Gessler1995-hz}. The key insight of
\textcite{Santiago2016-mu} is that the ratchet rate under draft is determined
by the probability of fixation $p_F(N_d, s)$
\parencite{Kimura1962-su,Malecot1948-zv} with the draft-rescaled effective
population size, i.e. $R = N U p_F(N_d, s)$. Given this equation for the
ratchet and Equation \eqref{eq:polygenic_Ne} for $N_d$ under draft, we have a
system of two non-linear equations that can be solved numerically for $N_d$ and
$R$ for each segment,

@@

where $V_a = (U-R)s$ as in Equation \eqref{eq:Va}. The predicted $V_a$, $R$,
and $N_d$ values represent the equilibria expected under a
mutation-selection-drift-draft process for neutral to strongly deleterious
additive mutations.

With the equilibrium $V_a$ calculated at each segment for a particular $\mu$
and $s$, we can estimate the reduction factor $B(x) = \nicefrac{N_d}{N}$ at any
genomic position $x$ (see Methods XXX). XXX

Since it is too computationally-intensive to numerically solve this system of
equations for all segments to estimate the reduction at every position

for every focal position $x$

% where,

% \begin{align}
%   V_a &= (U - R(x)) s & \text{\emph{fitness variance equation}} \\
%   Q^2 &= \frac{2}{(1-Z)(2-(2-M)Z)} & \text{\emph{linkage inflation factor}} \\
%   Z &= 1 - \frac{Us}{U-{R(x)}} & \text{\emph{}} \text{\emph{variance decay rate}}
% \end{align}

@@

@@

In our implementation of the theory of \textcite{Santiago2016-mu}, we calculate
the draft-effective population size $N_d = B N$ within a segment by solving a
system of two non-linear equations,

\begin{align}
  \label{eq:}
  {N}_{d} &= N \exp \left( -V_a \frac{Q^2}{2} \right) & \text{\emph{effective population equation}} \\
  R &= \frac{4N_eU s}{\exp(4 N_e s)-1}  & \text{\emph{substitution equation}} 
\end{align}

@@

\begin{align}
  %V(x) &= U s - 2 {R}(x) s & \text{\emph{fitness variance equation}} \\
  V_a &= (U  - 2 R) s & \text{\emph{fitness variance equation}} \\
  Q^2 &= \frac{2}{(1-Z)(2-(2-M)Z)} & \text{\emph{linkage inflation factor}} \\
  Z &= 1 - \frac{Us}{U-{R}} & \text{\emph{variance decay rate}}
\end{align}

and $U = \mu L$ and $M = r_\text{BP} L$ are the total mutation and
recombination rates for a segment $L$ basepairs long.

% Each mutation has a
% selection coefficient of $s$, for which we assume additive effects. Then, the
% local reduction factor is $b(x) = \nicefrac{N_e(x)}{N}$, and the per-basepair
% per-generation substitution rate is $\lambda_D = \nicefrac{R(x)}{L}$. Note that
% in the variance equation, the long-run variance is the balance between mutation
% and twice the loss due to substitution, $(U-2R)s$, since for selective balance
% $V(x) = 0$ for $s>0$, the per-basepair substitution rate must be half the mutation rate,
% since each substitution removes twice the variance introduced by a mutation in
% a diploid species.

Our software \texttt{bgspy} solves these two equations numerically for each
pre-specified segment across grids of mutation rates and selection
coefficients. The recombination rate in a segment is determined by a
user-supplied recombination map; segments that bridge a change in recombination
rate are split, and solved independently with the appropriate rate. This
pre-calculation step is done in parallel, and determines the equilibrium
additive genic fitness variation for each segment under a
mutation-selection-drift-draft process across the grids of parameters.

@@

The pre-computed equilibria are used to calculate the $B(x)$ maps across
parameter grids, which use in our comparisons to chromosome-scale forward
simulations and our composite-likelihood method. The reduction at a focal site
$x$ can be calculated as the product of all segments' contributing reduction
factors accounting for the recombination distances between the segment and
focal site. Additionally, to accommodate the estimation of separate DFEs for
different types of features, each $B(x)$ maps is

\begin{align}
    \log(B(x)) = - \sum_{i=1} \sum_{j=1} 
\end{align}

where $b(x, v)$ is a modified version of $b(x)$ that accounts for the
recombination between the segment $x$ and the neutral site $v$ (see XXX).

In practice, we calculate B' using the variables determined by solving the B'
equations for each mutation and selection coefficient in the grids. Since only
the analog of $Q^2(x)$, $Q^2(x, v)$ changes, the pre-computed substitution rate
(and thus local variance) can be re-used for each $v$. We calculate $B(v)$
across a grid of focal points along the chromosome, spaced 10kb apart.

@@

>>>>

\documentclass[11pt]{article}
\RequirePackage{fullpage}
%\RequirePackage[font=small,labelfont=bf]{caption}
\RequirePackage{amsmath,amssymb,amsthm}
\RequirePackage{graphicx}
\RequirePackage[hidelinks]{hyperref}
\RequirePackage{subcaption}
\RequirePackage{wasysym}
\RequirePackage{authblk}
\RequirePackage{bm}
\RequirePackage{bbm}

\RequirePackage{cleveref}
\RequirePackage{xr}
\externaldocument{supplementary}

%\RequirePackage[osf]{mathpazo}
\let\temp\rmdefault
\RequirePackage{mathpazo}
\let\rmdefault\temp

@@

%\title{Towards a Complete Model of the Negative Selection Process in Humans}
\title{An Evolutionary Quantitative Genetic Model of the Negative Selection Process in Humans}

@@

When mutations are only weakly deleterious, their allele frequencies are
strongly influenced by stochastic perturbations and their frequency
trajectories are no longer well-approximated by deterministic models. When
genetic drift is the only source of randomness in allele frequency change, the
relevant scale of stochastic perturbations is determined by the drift-effective
population size $N_e$ (e.g. due to only non-selective process). The insight of
nearly neutral theory \parencite{Ohta1971-gq,Ohta1992-yi} is determined by the
compound parameter $2N_e s$. When $2N_e s \gg 1$, the stochastic component of
allele frequency change is minuscule relative to selection and can be ignored;
this is why the factor that rescales the drift-effective population size under
the BGS model does not depend on $N_e$. However, when $2N_e s \le 1$, the
stochastic perturbations are on a scale equal to or greater than the changes
due to selection. In this regime, weakly deleterious alleles can drift up to
intermediate frequencies before their eventual loss or fixation. When this
occurs, classic BGS theory breaks down for several reasons. First, the ``delay
phase" is no longer negligible as lineages carrying weakly deleterious
mutations can persist on coalescent timescales. This distorts genealogies away
those expected under neutrality
\parencite{Przeworski1999-mb,OFallon2010-my,Higgs1995-xc}. Second, the
distribution of the number of deleterious mutations (and its corresponding
fitness distribution) are no longer stationary and become a traveling wave
\parencite{Rouzine2008-qz,Good2013-lp,Gessler1995-hz} towards reduced
population fitness (since beneficial and back mutations are ignored).
Consequently, individuals in the least-loaded class are stochastically lost,
fixing those mutations with a click of ``Muller's ratchet"
\parencite{Muller1964-ki}. Determining both the rate of Muller's ratchet
\parencite{Haigh1978-gt,Gordo2002-dr,Gessler1995-hz} and the shape of
genealogies under weak selection have been stubborn open problems in
evolutionary genetics.

@@

\begin{align}
    \label{eq:simple_Ne}
    N_e = \frac{2N}{V + 2}
\end{align}
%
where $V$ is the extra variance in offspring number.

However, unlike non-heritable variation in offspring number, the heritable
variation is autocorrelated across generations. At the individual level
Robertson considered, this is because offspring from large families tend to
beget many descendents themselves (and likewise with small families). The same
autocorrelation occurs at the genomic level, as the perturbations to a neutral
allele's trajectory from its particular fitness background tend to occur in the
same direction across generations as long as the linkage exists and the
selective environment is constant. Thus, the total additional heritable
variation in offspring number is the product of the equilibrium additive
fitness variation $V_A$ and an inflation factor $Q_t^2$ due to the build up of
autocorrelation to generation $t$. We let $Q^2 := Q_t^2$ as $t \to \infty$.
Intuitively, the product $V_A Q^2$ represents the expected total variance in
reproductive success a neutral mutation experiences over its lifetime in a
system with weak selection draft. Incorporating the impact of time-invariant
autocorrelation created by draft as a rescaled rate of drift is analogous to
using the Green--Kubo relation to find the transport coefficient in molecular
dynamics with velocity autocorrelation \parencite{Green1954-kl,Kubo1957-va}.

@@

(c.f. \cite{Robertson1961-ho,Santiago1995-hx}; see Supplementary Section
\ref{suppsec:theory} for a proof). In general, however, statistics such as
heterozygosity depend on the cumulative autocorrelation factor up to some time
$t$, $Q_t^2$ \parencite[p. 2111]{Santiago1998-bs}. This reflects the fact that
effective population size experienced by a mutation newly associated with a
fitness background is larger than the asymptotic effective population size,
since not much autocorrelation has accumulated in the stochastic perturbations
caused by drift yet. From a backwards-time perspective, this reflects the fact
that pairwise diversity (which is approximately heterozygosity when $2N\mu \ll
1$) depends on the pairwise coalescence rate per generation, which is not
constant under draft. The benefit of using Robertson's forward-time model of
draft is that the inflation factor is invariant with respect to the particular
fitness background the neutral allele becomes stochastically associated with.
By contrast, the difficulty with modeling draft backwards in time is that the
coalescence rates experienced by a lineage are not invariant to which lineage
was sampled due to its particular associated fitness background.

Equation \eqref{eq:main_Ne} is general, since different modes of selection and
linkage can be accommodated by different expressions for the inflation factor
$Q^2$ \parencite{Santiago1995-hx,Santiago1998-bs}. When fitness variation has a
multiplicative polygenic basis, as is often assumed for genome-wide negative
selection processes, the draft asymptotic effective population size experienced
by an arbitrary neutral site under the influence of all linked regions is,

@@

where the factor of one-half comes from ignoring weak associations from
unlinked regions and chromosomes (see Supplementary Section
\ref{suppsec:heritable-fitness}). In our genome-wide model, we consider the
summation in Equation \eqref{eq:polygenic_Ne} over non-overlapping segments $i
\in \{1, 2, \ldots, S\}$ each undergoing selection such that segment $i$
contributes additive fitness variance $V_{A,i}$ to the total additive genetic
fitness variance. Under equilibrium levels of fitness variation, the
autocorrelation function for a neutral allele associated with segment $i$ is
$C(t) = [(1-r_i)(1-\kappa_i)]^t$, where $r_i$ is the recombination fraction to
the segment and $\kappa_i$ is the rate that the associated fitness variance
decays due to selective dynamics. Then, the cumulative autocorrelation is,

\begin{align}
    Q_i &= 1 + \sum_{j=1}^\infty \left[(1-r_i)(1-\kappa_i)\right]^j \nonumber \\
        &= \frac{1}{\kappa_i + r_i(1-\kappa_i)}.
\end{align}

@@

which is identical to the genome-wide model of background selection used in
previous studies \parencite{McVicker2009-ax,Elyashiv2016-vt,Murphy2022-sj}.
Thus, the classic background selection model is a special case of the more
general theory of Santiago and Caballero (\citeyear{Santiago2016-mu}), which
they had shown previously (\citeyear{Santiago1998-bs}).

When selection is weak, however, the additive fitness variance under the
classic BGS model is no longer accurate. \textcite{Santiago2016-mu} suggested
that this is due to the loss of fitness variation that occurs when a
segregating site fixes and its heterozygosity becomes zero. If we let $R$
represent the fixation rate (i.e. ratchet rate) in the region per generation,
each fixation removes the equivalent amount of equilibrium variation put in by
mutation. Thus, the steady-state genic variance under mutation and negative
selection is (omitting the segment index $i$ for clarity),

@@

where the condition $V_a \ge 0$ is met when the probability of fixation is less
than or equal to the neutral fixation probability of $\nicefrac{1}{2N}$, which
is held when considering deleterious mutations. This equation connects the
equilibrium additive genic fitness variance to the flux of new variation in due
to new deleterious mutations and the flux out due to their substitution and the
decline in mean population fitness. When $R=0$, selection is so strong it
cannot fix, and the equilibrium fitness variation is due entirely to young rare
mutations before their extinction $V_a = V_a^{BGS} \approx Us$. Santiago and
Caballero derive Equation \eqref{eq:Va} through Fisher's Fundamental Theorem of
Natural Selection, but we find an alternative proof (\cite{Higgs1995-xc}; see
Supplementary Materials Section \ref{supp:weak-strong}). We also find that the
steady-state additive genic variance in Equation \eqref{eq:Va} results from
diffusion models with a flux of mutations into discrete sites
(\cite{Kimura1969-jw}).

@@

While using Equation \eqref{eq:Va} in Equation \eqref{eq:main_Ne} leads to a
prediction for the draft-effective population size $N_d$, closed-form
expressions for the rate of the ratchet $R$ have generally been hard to find
\parencite{Haigh1978-gt,Higgs1995-xc,Gessler1995-hz}. The key insight of
\textcite{Santiago2016-mu} is that the ratchet rate under draft is determined
by the probability of fixation $p_F(N_d, s)$
\parencite{Kimura1962-su,Malecot1948-zv} using the draft-rescaled effective
population size, i.e. $R = N U p_F(N_d, s)$. Given this equation for the
ratchet and Equation \eqref{eq:polygenic_Ne} for $N_d$ under draft, we have a
system of two non-linear equations that can be solved numerically for $N_d$ and
$R$ for each segment,

@@

where $V_a = (U-R)s$ as in Equation \eqref{eq:Va}. The predicted $V_a$, $R$,
and $N_d$ values represent the equilibria expected under a
mutation-selection-drift-draft process for neutral to strongly deleterious
additive mutations. The collection of these $V_a$ and $R$ equilibria can then
be used to calculate the reduction at an arbitrary position in the genome (see
Methods

With the equilibrium $V_a$ calculated at each segment for a particular $\mu$
and $s$, we can estimate the reduction factor $B(x) = \nicefrac{N_d}{N}$ at any
genomic position $x$ (see Methods XXX).

@@

Measuring selection in the Genome Versus Finding Selection in the Genome

@@

Our software \texttt{bgspy} first calculates the equilibrium additive genic
fitness variation $\widetilde{V}_a$ and ratchet rate $\widetilde{R}$ for each
user-specified segments in the genome. These equilibria are calculated across
grids of mutation rate weighted by the DFE $m_i$ and selection coefficient
$s_j$, by numerically solving the following system of equations,

\begin{align}
  \label{eq:}
  {N}_{d} &= N \exp \left( -V_a \frac{Q^2(m_i, s_j)}{2} \right) & \text{\emph{effective population equation}} \\
  R &= \frac{4N_dU s_j}{\exp(4 N_d s_j)-1}  & \text{\emph{substitution equation}} 
\end{align}

@@

\begin{align}
  %V(x) &= U s - 2 {R}(x) s & \text{\emph{fitness variance equation}} \\
  V_a &= (U - 2 R) s_j & \text{\emph{fitness variance equation}} \\
  Q^2(m_i, s_j) &= \frac{2}{(1-Z)(2-(2-M)Z)} & \text{\emph{linkage inflation factor}} \\
  Z &= 1 - \frac{Us_j}{U-{M}} & \text{\emph{variance decay rate}}
\end{align}
%
and $U = m_i L$ and $M = r_\text{BP} L$ are the total mutation and
recombination rates in the segment. A detailed derivation of these equations
can be found in Supplementary Section \ref{suppsec:theory}. The recombination
rate in a segment is determined by a user-supplied recombination map.

@@

We use these pre-computed equilibria to calculate the reduction map $B(x; m_i,
s_j)$ at positions $x$ across the mutation grids described above. Since we
assume multiplicative fitness, the reduction is the product of each segment's
contribution accounting for the recombination is,

\begin{align}
    B(x; m_i, s_j) = \exp\left(- \frac{1}{2}\sum_{g \in G} \sum_{i=1}^{n_s} V_g(m_i, s_j) Q_g^2(m_i, s_j, r_{x, g})\right)
\end{align}

where $r_{x, g}$ is the recombination fraction between the focal site and
segment $g$. A separate reduction map is calculated for all features $G$ within
a specific feature type. Our B' maps are calculated for $\log_{10}$-spaced
grids over $10^{-1} \le s \le 10^{-8}$ and $10^{-11} \le m \le 10^{-7}$, in
10kb increments across the genome.

\subsection*{Composite Likelihood}
\label{sec:methods-likelihood}

\begin{align}
    \log\left(B(x; W, s_j) \right) = - \frac{1}{2} \sum_{g \in G} \sum_{i=1}^{n_s} V_g(\mu W_{j, k(g)}, s_j) Q_g^2(m_i, s_j, r_{x, g})
\end{align}

@@

\subsection*{Human Population Genomic Diversity Estimates}

We estimate pairwise diversity for Yoruba (YRI), European (CEU), and Han
Chinese (CHB) ancestry individuals in the high-coverage 1000 Human Genomes
dataset (XXX). We
